Autonomous Aerial for Topological Mapping of Mars Environments

### 2018-06-10 Conference/SCITECH19/SCITECH19.tex
edit done for results and conclusion

\author{Evan Kaufman\footnote{Graduate Research Assistant} and Taeyoung Lee\footnote{Associate Professor, AIAA Member Grade (if any)}}
\affil{Department of Mechanical and Aerospace Engineering, The George Washington University, Washington, DC, 20052}
% TODO: funding source

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements. There are two major programs, referred to as \emph{nodes} in ROS, used during the simulation: mapping and exploration. The mapping node takes measurements from a 3D laser scanner and pairs those with the sensor transformation relative to Mars using the ROS Transform Message Filters package. Then, it builds a 3D probabilistic map using \refeqn{RayISMAnswer}-\refeqn{Unnormalized}. The mapping node sends updates from the probabilistic map to the exploration node, which decomposes the map into $ m_\text{reduced}$ according to \refeqn{Proj3DMapComb}, and builds a cost map based on Dijkstra's search to determine collision-free trajectory costs for all pose candidates. Finally, it applies \refeqn{RcStar}, \refeqn{BumpFunRecedingHorizon}, and \refeqn{CandidateLocationOptimization} to update the desired robot trajectory on a receding-horizon. An overview of the process is illustrated in Fig. \ref{fig:NodesDiagram}.

@@

A 3D environment of Mars is simulated in Gazebo. A height map~\cite{mapaplanet} is used to generate a contoured surface, and the corresponding picture of Mars is draped over this contour, shown in Fig. \ref{fig:MarsGazebo}. A laser scanner was also simulated in Gazebo. In the horizontal direction, the sensor has limits $\Psi=120\degree$ with a total of $1000$ measurement rays inside, the sensor is fixed at angle $\tilde{\psi}=45\degree$, and $n_\psi=16$ sample measurements are used. In the vertical direction, the sensor also has limits $\Theta=120\degree$ with a total of $1000$ measurement rays inside, but the sensor is fixed at angle $\tilde{\theta}=30\degree$, and $n_\psi=7$ sample measurements are used. These ray samples are taken from candidate locations separated $1$ m apart in each dimension.

@@

The map parameters are also important to the success of the exploration. The full map has dimensions $20$ m$\times20$ m$\times5$ m in the Mars-fixed frame, with cell edge length $\alpha=0.075$ m. The reduced map for collision-avoidance and motion planning has cells $k=3$ times the size ($0.225$ m), so $k^3=27$ cells are considered in \refeqn{Proj3DMapComb}. The bump functions use $f_\text{max}=1.0$, $f_\text{far}=0.1$, and $\beta=0.1$ to account for travel costs with \refeqn{BumpFunRecedingHorizon}. The receding horizon optimal time $d_\text{opt}$ is based on a fixed robot velocity of $0.5$ m/sec and the computation time varies from $0.6$ sec to $1.0$ sec.

The simulation is run twice. Case 1 is as described in this paper. Case 2 is identical, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} provided useful effective information during level flight. The resulting occupancy grid maps and complete map entropy are shown in Figs. \ref{fig:mars3Dogm} and \ref{fig:mars3Dentropy}, respectively.

@@

NEXT: ADD 3 PARAGRAPHS

In both cases, the ...

However, the choice of occupancy grid map introduced an interesting tradeoff.

In short,

% software structure
% Numerical Result
  % reduced map used for entropy
  % full map used for entropy

@@

>>>>

\author{Evan Kaufman\footnote{Graduate Research Assistant} and Taeyoung Lee\footnote{Associate Professor, AIAA Member Grade (if any)}}% TODO: update if AIAA member
\affil{Department of Mechanical and Aerospace Engineering, The George Washington University, Washington, DC, 20052}
% TODO: funding source

@@

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework (Kinetic distribution), and Gazebo 8 serves as the simulator for the physical objects and measurements. There are two major programs, referred to as \emph{nodes} in ROS, used during the simulation: mapping and exploration. The mapping node takes measurements from a 3D laser scanner and pairs those with the sensor transformation relative to Mars using the ROS Transform Message Filters package. Then, it builds a 3D probabilistic map using \refeqn{RayISMAnswer}-\refeqn{Unnormalized}. The mapping node sends updates from the probabilistic map to the exploration node, which decomposes the full map $m$ into $ m_\text{reduced}$ according to \refeqn{Proj3DMapComb}, and builds a cost map based on Dijkstra's search to determine collision-free trajectory costs for all pose candidates. Finally, it applies \refeqn{RcStar}, \refeqn{BumpFunRecedingHorizon}, and \refeqn{CandidateLocationOptimization} to update the desired robot trajectory on a receding-horizon. An overview of the process is illustrated in Fig. \ref{fig:NodesDiagram}.

@@

A 3D environment of Mars is simulated in Gazebo. A height map~\cite{mapaplanet} is used to generate a contoured surface, and the corresponding picture of Mars is draped over this contour, shown in Fig. \ref{fig:MarsGazebo}. A 3D laser scanner is also simulated in Gazebo. In the horizontal direction, the sensor has limits $\Psi=120\degree$ with a total of $1000$ measurement rays inside, the sensor is fixed at angle $\tilde{\psi}=45\degree$, and $n_\psi=16$ sample measurements are used. In the vertical direction, the sensor also has limits $\Theta=120\degree$ with a total of $1000$ measurement rays inside, but the sensor is fixed at angle $\tilde{\theta}=30\degree$, and $n_\psi=7$ sample measurements are used. These ray samples are taken from each candidate location, which are separated $1$ m apart in each of the $3$ dimensions.

@@

The map parameters are also important to the success of the exploration. The full map has dimensions $20$ m $\times$ $20$ m $\times$ $5$ m in the Mars-fixed frame, with cell edge length $\alpha=0.075$ m. The reduced map for collision-avoidance and motion planning has cells $k=3$ times the size ($0.225$ m), so $k^3=27$ cells are considered in \refeqn{Proj3DMapComb}. The bump functions use $f_\text{max}=1.0$, $f_\text{far}=0.1$, and $\beta=0.1$ to account for travel costs with \refeqn{BumpFunRecedingHorizon}. The receding horizon optimal time $d_\text{opt}$ is based on a fixed robot velocity of $0.25$ m/sec and the computation time varies from $0.6$ sec to $1.0$ sec.

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps and complete map entropy are shown in Figs. \ref{fig:mars3Dogm} and \ref{fig:mars3Dentropy}, respectively.

@@

In both cases, the robot built the 3D probabilistic map of the $2000$ cubic meter space composed of $4.74\times10^6$ grid cells. The maps were mostly complete within $10$ minutes. The $\tilde{\theta}=30\degree$ downward viewing angle captured the ground nicely, as candidate attitudes tended to direct the onboard sensor toward uncertain regions on the surface of Mars. The proposed approach provided collision-free mapping and autonomous exploration in real-time.

However, the choice of occupancy grid map used for entropy predictions introduced an interesting tradeoff. In Case 1, when the full probabilistic map $m$ was used in \refeqn{Iscan}, regions where the grid cells were partially-known were frequently reconsidered until the space was well-known. Conversely in Case 2, when $m_\text{reduced}$ was used instead, the robot repeatedly left spaces that were missing a few grid cells to visit new terrain. This is because $m_\text{reduced}$ had some cells with large occupancy probabilities based on \refeqn{Proj3DMapComb}, which allowed some grid cells of $m$ enclosed within a cell of $m_\text{reduced}$ to be uncertain. The exploration policy of Case 2 incorrectly assumed these regions were well-known. Ironically, this false assumption sometimes actually led to greater information gains when the vehicle moved on to unvisited terrain. Here, the exploration policy of Case 2 suspended operations once expected information gains were insignificant, which happened after about $10$ minutes. However with Case $1$, which used $m$ for computing expected entropy, the exploration continued for an additional $10$ minutes, overall decreasing total map entropy further, generating a more complete occupancy grid of the surface of Mars.

In short, the proposed 3D probabilistic occupancy grid mapping and autonomous exploration were simulated successfully in real-time over the surface of Mars using ROS and Gazebo. Choosing $m$ for entropy predictions produced a more-complete map, but choosing $m_\text{reduced}$ was sometimes beneficial for exploring new terrain faster, while forgoing map completeness.

@@

In this paper, we proposed an approach to autonomously explore the complex and uncertain terrain of Mars. The exploration strategy is based on flying vehicles near the surface of Mars, where their exploration policy is based on expected information gain from Shannon's entropy of a probabilistic map, and travel costs from Dijkstra's algorithm. The autonomous exploration scheme was applied in real-time, following a receding-horizon framework, so the map could be generated as quickly as possible. Numerical simulations demonstrated the efficacy of the approach, showing two possible versions of the 3D exploration with differing behavior in probabilistic map accuracy and exploration speed.
